Quantum Mechanics Assignment Three

### 2016-02-02 quantum/latex/a4.tex
stuff
Add completed? a4.tex

\begin{align*}
  E_n^{(1)} &= \bra{n}H'\ket{n}\\
  &= \int_0^L 2\sin^2\left(\frac{n\pi x}{L}\right)V_0\delta(x-L/2)dx\\
  &= 2V_0\sin^2\left(\frac{n\pi}{2}\right)\\
  \begin{cases}
    2V_0 & \mbox{n is odd}\\
    0 & \mbox{n is even}\\
  \end{cases}\\
\end{align*}

@@

>>>>

\begin{align*}
  E_n^{(1)} &= \bra{n}H'\ket{n}\\
  &= \int_0^L 2\sin^2\left(\frac{n\pi x}{L}\right)V_0\delta(x-L/2)dx\\
  &= 2V_0\sin^2\left(\frac{n\pi}{2}\right)\\
  &= \begin{cases}
    2V_0 & \mbox{n is odd}\\
    0 & \mbox{n is even}\\
  \end{cases}\\
\end{align*}

@@

Now we solve for the perturbed states. We begin with the order-one correction equation:\\

\begin{align*}
  \left(H_0 - E_n^0\right)\ket{2^{(1)}} &= \left(E_n^{(1)} - H'\right)\ket{n^{(0)}}\\
\end{align*}

We then populate this equation with our values, solving for $E_1^1$:\\

\begin{align*}
  \begin{pmatrix}
    0 & 0 & 0 & 0\\
    0 & 0 & 0 & 0\\
    0 & 0 & 2 & 0\\
    0 & 0 & 0 & 4\\
  \end{pmatrix}
  \begin{pmatrix}
    c_{11}\\
    c_{22}\\
    c_{33}\\
    c_{44}\\
  \end{pmatrix}
  &=
  \begin{pmatrix}
    E_1^1 - H_{11}' & -H_{12}' & -H_{13}' & -H_{14}'\\
    -H_{21}' & E_1^1 - H_{22}' & -H_{23}' & -H_{24}'\\
    -H_{31}' & -H_{32}' & E_1^1 - H_{33}' & -H_{34}'\\
    -H_{41}' & -H_{42}' & -H_{43}' & E_1^1 - H_{44}'\\
  \end{pmatrix}
  \begin{pmatrix}
    \alpha\\
    \beta\\
    0\\
    0\\
  \end{pmatrix}
\end{align*}

This leads to the following system of equations:\\

\begin{align*}
  \left(E_1^{(1)} - H_{11}'\right)\alpha + H_{12}'\beta &= 0\\
  H_{21}'\alpha + \left(E_1^{(1)} - H_{22}'\right)\beta &= 0\\
\end{align*}

which can be turned into an energy eigenvalue equation:\\

\begin{align*}
  \begin{pmatrix}
    H_{11}' & H_{12}'\\
    H_{21}' & H_{22}'\\
  \end{pmatrix}
  \begin{pmatrix}
    \alpha\\
    \beta\\
  \end{pmatrix}
  &=
  E_1^{(1)}
  \begin{pmatrix}
    \alpha\\
    \beta\\
  \end{pmatrix}\\
  \begin{pmatrix}
    0 & \epsilon\\
    \epsilon & 0\\
  \end{pmatrix}
  \begin{pmatrix}
    \alpha\\
    \beta\\
  \end{pmatrix}
  &=
  E_1^{(1)}
  \begin{pmatrix}
    \alpha\\
    \beta\\
  \end{pmatrix}\\
\end{align*}

We then solve for the eigenvalues of this system and get the following result:

\begin{align*}
  E_1^{(1)} &= \pm \epsilon\\
\end{align*}
